---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# keywordApp

<!-- badges: start -->
<!-- badges: end -->

The objective of keywordApp is to streamline the analysis process for datasets generated by Google Keyword. This package provides a simple app to which you can upload, and interrogate the contents of, your dataset.

## Installation

You can install the development version of keywordApp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AoifeRyan-sc/keywordApp")
```

## Launching the App

Launching the app is quite straightforward:

```{r example, eval = FALSE}
keywordApp::run_app()
```

Once you have launched the app you should upload your dataset by clicking the "Browse" button on the top left corner of the page. Datasets should be csv, tsv, or xlsx.
